Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-04-01 doc/peakcharacterization_manuscript.Rmd
added set intersection and mz differences
I think this closes #11

threonine_ratioplot = ggplot(threonine_ratios, aes(x = ratio, y = diff, color = source, size = n_missing)) +
    geom_point() +
    theme(legend.position = c(0.7, 0.8)) +
    labs(x = "Pairwise Comparison",
         y = "Peak-Peak NAP - Height Differences") +
  theme(axis.title.y = element_text(size = nap_fontsize))

@@

figure_count$increment("unassigned_upset")

tar_load(um_peaks_1ecf)
tar_load(um_peaks_97lipid)
```

@@

>>>>

threonine_ratioplot = ggplot(threonine_ratios, aes(x = ratio, y = diff, color = source, size = n_missing)) +
    geom_point() +
    theme(legend.position = c(0.7, 0.75)) +
    labs(x = "Pairwise Comparison",
         y = "Peak-Peak NAP - Height Differences") +
  theme(axis.title.y = element_text(size = nap_fontsize))

@@

figure_count$increment("unassigned_upset")
figure_count$increment("assigned_mz_diff")

tar_load(um_peaks_1ecf)
tar_load(um_peaks_97lipid)
tar_load(ass_peaks_1ecf)
tar_load(ass_peaks_97lipid)
```

@@

::: {custom-style="MDPI_5.2_figure"}
```{r assigned_mz_diff, dn_id = figure_count}
diffs_1ecf = ass_peaks_1ecf$peaks %>%
  dplyr::mutate(source = factor(source, levels = c("scanlevel", "xcalibur", "msnbase"), ordered = TRUE))
diffs_97lipid = ass_peaks_97lipid$peaks %>%
  dplyr::mutate(source = factor(source, levels = c("scanlevel", "xcalibur", "msnbase"), ordered = TRUE))

diffs_plot = (diffs_1ecf %>%
                ggplot(aes(x = mz_diff)) +
  geom_histogram(bins = 30) +
  facet_wrap(~ source, ncol = 1) +
  labs(x = "m/z Difference")) |
  (diffs_97lipid %>%
     ggplot(aes(x = mz_diff)) +
     geom_histogram(bins = 30) +
     facet_wrap(~ source, ncol = 1) +
     labs(x = "m/z Difference")) +
  plot_annotation(tag_levels = "A")
diffs_plot
```
:::

::: {custom-style="MDPI_5.1_figure_caption"}
`r figure_count$label_text("assigned_mz_diff")`.
Histograms of the m/z differences to the assigned and matched peak for 1ecf (**A**) and 97lipid (**B**).
:::
